---
title: "Simple Predictions: Car Distance & Petal Length"
output: 
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_float: true
    df_print: kable
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

After I learned to use RapidMiner I  moved on to learning R. This is my first report (:D), in which I was asked to do a basic exploratory data analysis, in which I would use two independent linear regression models to make some basic predictions. Furthermore, I was also tasked with reviewing some code having complete the linear regressions and correcting the mistakes in the code.

## 1. Car Distance

The first regression concerns the distance traveled by a set of cars of which the average speed they have been traveling is known. As can be expected the distance traveled is strongly correlated with the average speed they have been driving and the correlation seems to be estimated quite well by a linear regression model

### Data Cars Summary
```{r echo=FALSE}
#Print Summary of Data

cars <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/2. Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/cars.csv")

summary(cars)
````

### Prediction Car Distance
```{r echo=FALSE}
# Print predictions of distance

cars$name.of.car <- as.factor(cars$name.of.car)


names(cars) <-c("namecar", "speedcar","distancecar")

set.seed(123)

trainsize<-round(nrow(cars)*.7)

testsize<-nrow(cars)-trainsize

training_indices<-sample(seq_len(nrow(cars)),size=trainsize)
trainset<-cars[training_indices,]
testset<-cars [-training_indices,]

distancebyspeed<-lm(distancecar ~ speedcar, trainset)

Preddistance<-predict(distancebyspeed,testset)

Preddistance
````

## 2 Petal Length

While the second regression is completely unrelated to the first the methodology applied is the same which demonstrates the versatility of regression models for all types of numeric data sets. The second regression models the petal’s length of an iris flower based on the petal’s with.

### Petal Data Summary

````{r echo=FALSE}
# Print summary of data

IrisDataset <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/2. Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/iris.csv")

summary(iris) 
````

### Petal Length Prediction

````{r echo=FALSE}
# Print predictions of petal length

iris$Species <- as.numeric(iris$Species)

set.seed(123)

trainSize <- round(nrow(iris) * 0.7)

testSize <- nrow(iris)-trainSize

set.seed(123)

training_indices<-sample(seq_len(nrow(iris)),size=trainSize)

trainset<-iris[training_indices,]

testset<-iris [-training_indices,]

LinearModel<- lm(Petal.Width ~ Petal.Length, trainset)

prediction<-predict(LinearModel, testset)

prediction

````


## 3 Petal Length Code Correction

Lastly I was tasked with correcting some faulty code a fellow student had made, to predict the petal length. The corrections include both the mistakes and the corrected version of the code in green.

 <p style="color:red">  1.install.packages(readr) </p>
<p style="color:green"> *Was missing:* **“ “**  Should be: **install.packages("readr")** <p style="color:green">

<p style="color:red">  2.library("readr") </p>
<p style="color:green"> *Does not need* **“ “** Should be: **library(readr)** <p style="color:green">

<p style="color:red">  3.IrisDataset <- read.csv(iris.csv) </p>
<p style="color:green"> *Was missing complete directory:*  Should be: **IrisDataset <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/iris.csv")** <p style="color:green">


<p style="color:red"> 4.attributes(IrisDataset) <p style="color:red">
<p style="color:green"> *Seems to work but better without Dataset* Should be: **attributes(iris)** <p style="color:green">

<p style="color:red"> 5.summary(risDataset) <p style="color:red">
<p style="color:green"> Should be: **summary(iris)** <p style="color:green">

<p style="color:red"> 6.str(IrisDatasets) <p style="color:red">
<p style="color:green"> Should be: **str(iris)** <p style="color:green">

<p style="color:red"> 7.names(IrisDataset) <p style="color:red">
<p style="color:green"> Should be: **names(iris)** <p style="color:green">

<p style="color:red"> 8.hist(IrisDataset$Species) <p style="color:red">

<p style="color:green">*need to transform to numeric*
Should be: **iris$Species <- as.numeric(iris$Species)**
Should be: **hist(iris$Species)** <p style="color:green">

<p style="color:red"> 9.plot(IrisDataset$Sepal.Length <p style="color:red">

<p style="color:green"> Should be:**plot(iris$Sepal.Length)** <p style="color:green">

<p style="color:red"> 10.qqnorm(IrisDataset) <p style="color:red">

<p style="color:green"> *Missing what attribute should be plotted as we are interested in petal’s length & width plot these*
Should be: **qqnorm(iris$Petal.Length)**
Should be: **qqnorm(iris$Petal.Width)** <p style="color:green">


<p style="color:red"> 11.IrisDataset$Species<- as.numeric(IrisDataset$Species) <p style="color:red">
<p style="color:green"> *Already previously done (need to be just iris)* <p style="color:green">

<p style="color:red"> 12.set.seed(123) <p style="color:red">
<p style="color:green"> *No mistake found (yet)* <p style="color:green">

<p style="color:red"> 13.trainSize <- round(nrow(IrisDataset) * 0.2) <p style="color:red">
<p style="color:green"> Should be: **iris (not IrisDataset)**
*Normally we choose a large percentage of the data for training  use 0.7*
Should be: **trainSize <- round(nrow(iris) * 0.7)** <p style="color:green">

<p style="color:red"> 14.testSize <- nrow(IrisDataset) – trainset <p style="color:red">
<p style="color:green"> Should be: **testSize <- nrow(iris)-trainSize** <p style="color:green">

<p style="color:red"> 15.trainSizes <p style="color:red">
<p style="color:green"> Should be: **trainSize** <p style="color:green">

<p style="color:red"> 16.testSize <p style="color:red">
<p style="color:green"> Seems correct
Followed by: **training_indices<-sample(seq_len(nrow(iris)),size=trainSize)**
Followed by: **set.seed(123)** <p style="color:green">

<p style="color:red"> 17.trainSet <- IrisDataset[training_indices, ] <p style="color:red">
<p style="color:green"> Should be: **trainset<-iris[training_indices,]** <p style="color:green">

<p style="color:red"> 18.testSet <- IrisDataset[-training_indices, ] <p style="color:red">
<p style="color:green"> Should be: **testset<-iris [-training_indices,]** <p style="color:green">

<p style="color:red"> 19.set.seed(405) <p style="color:red">
<p style="color:green"> *Already have in the beginning why need twice?*
Should be: **set.seed(123)** <p style="color:green">

<p style="color:red"> 20.trainSet <- IrisDataset[training_indices, ] <p style="color:red">
<p style="color:green"> *Already have above* <p style="color:green">

<p style="color:red"> 21.testSet <- IrisDataset[-training_indices, ] <p style="color:red">
<p style="color:green"> *Already have above* <p style="color:green">

<p style="color:red"> 22.LinearModel<- lm(trainSet$Petal.Width ~ testingSet$Petal.Length) <p style="color:red">
<p style="color:green"> Should be: **LinearModel<- lm(Petal.Width ~ Petal.Length, trainset)** <p style="color:green">

<p style="color:red"> 23.summary(LinearModel) <p style="color:red">
<p style="color:green"> *Seems correct* <p style="color:green">

<p style="color:red"> 24.prediction<-predict(LinearModeltestSet) <p style="color:red">
<p style="color:green"> Should be: **prediction<-predict(LinearModel, testset)** <p style="color:green">

<p style="color:red"> 25.predictions <p style="color:red">
<p style="color:green"> *seems correct* <p style="color:green">
