````
---
title: "Task2.1: Simple Predictions"
author: "Tom"
date: "2020-03-04"
output: html_document
--- 
```

````
**Predictions: Car Distance & Petal length**
<p style="color:blue">  1.Car Distance Summary <p style="color:blue">

````

```{r echo=FALSE}
#Print Summary of Data

cars <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/cars.csv")

summary(cars)
```

````
<p style="color:blue">  2.Car Distance Prediction <p style="color:blue">
````

```{r echo=FALSE}
# Print predictions of distance

cars$name.of.car <- as.factor(cars$name.of.car)


names(cars) <-c("namecar", "speedcar","distancecar")

set.seed(123)

trainsize<-round(nrow(cars)*.7)

testsize<-nrow(cars)-trainsize

training_indices<-sample(seq_len(nrow(cars)),size=trainsize)
trainset<-cars[training_indices,]
testset<-cars [-training_indices,]

distancebyspeed<-lm(distancecar ~ speedcar, trainset)

Preddistance<-predict(distancebyspeed,testset)

Preddistance
```

````
<p style="color:blue">  3. Petal Distance Summary <p style="color:blue">
````

```{r echo=FALSE}
# Print summary of data

IrisDataset <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/iris.csv")

summary(iris) 
```

````
<p style="color:blue">  4.Petal Length Prediction <p style="color:blue"> 
````


```{r echo=FALSE}
# Print predictions of petal length

iris$Species <- as.numeric(iris$Species)

set.seed(123)

trainSize <- round(nrow(iris) * 0.7)

testSize <- nrow(iris)-trainSize

set.seed(123)

training_indices<-sample(seq_len(nrow(iris)),size=trainSize)

trainset<-iris[training_indices,]

testset<-iris [-training_indices,]

LinearModel<- lm(Petal.Width ~ Petal.Length, trainset)

prediction<-predict(LinearModel, testset)

prediction

```


<p style="color:blue">  3.Petal Length Script Correction  <p style="color:blue"> 

 <p style="color:red">  1.install.packages(readr) </p>
<p style="color:green"> *Was missing:* **“ “**  Should be: **install.packages("readr")** <p style="color:green">

<p style="color:red">  2.library("readr") </p>
<p style="color:green"> *Does not need* **“ “** Should be: **library(readr)** <p style="color:green">

<p style="color:red">  3.IrisDataset <- read.csv(iris.csv) </p>
<p style="color:green"> *Was missing complete directory:*  Should be: **IrisDataset <- read.csv("C:/Users/Thomas S/Documents/Ubiqum/Data Analytics 2/R Tutorial Data/R Tutorial Data Sets/iris.csv")** <p style="color:green">


<p style="color:red"> 4.attributes(IrisDataset) <p style="color:red">
<p style="color:green"> *Seems to work but better without Dataset* Should be: **attributes(iris)** <p style="color:green">

<p style="color:red"> 5.summary(risDataset) <p style="color:red">
<p style="color:green"> Should be: **summary(iris)** <p style="color:green">

<p style="color:red"> 6.str(IrisDatasets) <p style="color:red">
<p style="color:green"> Should be: **str(iris)** <p style="color:green">

<p style="color:red"> 7.names(IrisDataset) <p style="color:red">
<p style="color:green"> Should be: **names(iris)** <p style="color:green">

<p style="color:red"> 8.hist(IrisDataset$Species) <p style="color:red">

<p style="color:green">*need to transform to numeric*
Should be: **iris$Species <- as.numeric(iris$Species)**
Should be: **hist(iris$Species)** <p style="color:green">

<p style="color:red"> 9.plot(IrisDataset$Sepal.Length <p style="color:red">
<p style="color:green"> Should be: **plot(iris$Sepal.Length)** <p style="color:green">

<p style="color:red"> 10.qqnorm(IrisDataset) <p style="color:red">

<p style="color:green"> *Missing what attribute should be plotted as we are interested in petal’s length & width plot these*
Should be: **qqnorm(iris$Petal.Length)**
Should be: **qqnorm(iris$Petal.Width)** <p style="color:green">


<p style="color:red"> 11.IrisDataset$Species<- as.numeric(IrisDataset$Species) <p style="color:red">
<p style="color:green"> *Already previously done (need to be just iris)* <p style="color:green">

<p style="color:red"> 12.set.seed(123) <p style="color:red">
<p style="color:green"> *No mistake found (yet)* <p style="color:green">

<p style="color:red"> 13.trainSize <- round(nrow(IrisDataset) * 0.2) <p style="color:red">
<p style="color:green"> Should be: **iris (not IrisDataset)**
*Normally we choose a large percentage of the data for training  use 0.7*
Should be: **trainSize <- round(nrow(iris) * 0.7)** <p style="color:green">

<p style="color:red"> 14.testSize <- nrow(IrisDataset) – trainset <p style="color:red">
<p style="color:green"> Should be: **testSize <- nrow(iris)-trainSize** <p style="color:green">

<p style="color:red"> 15.trainSizes <p style="color:red">
<p style="color:green"> Should be: **trainSize** <p style="color:green">

<p style="color:red"> 16.testSize <p style="color:red">
<p style="color:green"> Seems correct
Followed by: **training_indices<-sample(seq_len(nrow(iris)),size=trainSize)**
Followed by: **set.seed(123)** <p style="color:green">

<p style="color:red"> 17.trainSet <- IrisDataset[training_indices, ] <p style="color:red">
<p style="color:green"> Should be: **trainset<-iris[training_indices,]** <p style="color:green">

<p style="color:red"> 18.testSet <- IrisDataset[-training_indices, ] <p style="color:red">
<p style="color:green"> Should be: **testset<-iris [-training_indices,]** <p style="color:green">

<p style="color:red"> 19.set.seed(405) <p style="color:red">
<p style="color:green"> *Already have in the beginning why need twice?*
Should be: **set.seed(123)** <p style="color:green">

<p style="color:red"> 20.trainSet <- IrisDataset[training_indices, ] <p style="color:red">
<p style="color:green"> *Already have above* <p style="color:green">

<p style="color:red"> 21.testSet <- IrisDataset[-training_indices, ] <p style="color:red">
<p style="color:green"> *Already have above* <p style="color:green">

<p style="color:red"> 22.LinearModel<- lm(trainSet$Petal.Width ~ testingSet$Petal.Length) <p style="color:red">
<p style="color:green"> Should be: **LinearModel<- lm(Petal.Width ~ Petal.Length, trainset)** <p style="color:green">

<p style="color:red"> 23.summary(LinearModel) <p style="color:red">
<p style="color:green"> *Seems correct* <p style="color:green">

<p style="color:red"> 24.prediction<-predict(LinearModeltestSet) <p style="color:red">
<p style="color:green"> Should be: **prediction<-predict(LinearModel, testset)** <p style="color:green">

<p style="color:red"> 25.predictions <p style="color:red">
<p style="color:green"> *seems correct* <p style="color:green">









